\documentclass[10pt]{article}
\usepackage[margin=0.5cm]{geometry}
\usepackage[dvipsnames,cmyk]{xcolor}
\usepackage{libertine}
%\usepackage[sc]{mathpazo}
\usepackage{hyperref,ulem,contour}
\usepackage{tikz}
\usepackage{paralist}
\usepackage{titlesec}
\usetikzlibrary{calc}

\newcommand{\blankline}{\quad\pagebreak[2]}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\hrefgreen}[2]{\href{#1}{\color{ForestGreen}\uline{\phantom{#2}}\llap{\contour{white}{#2}} }}
\newcommand{\hrefblack}[2]{\href{#1}{\color{Black}\uline{\phantom{#2}}\llap{\contour{Cerulean}{#2}} }}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{.98\columnwidth}{1pt}%
         \end{minipage}}

\titleformat{\section}{\large\scshape}{\thesection}{1.25em}{}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

\newenvironment{outerlist2}[1][\enskip\textbullet]{\begin{compactitem}[#1]}{\end{compactitem}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

\newcommand{\tpc}{\textbf{\textperiodcentered}\,}

\pagestyle{empty}     

\begin{document}
\begin{tikzpicture}[remember picture,overlay]
    \path (0.95\textwidth+0.5cm , 1.5) coordinate (p1) {};
    \path (0.65\textwidth+0.25cm, 1.5) coordinate (p2) {};
    \path (0.95\textwidth+0.5cm , -30) coordinate (p3) {};
    \path (0.65\textwidth+0.25cm, -30) coordinate (p4) {};
    %\path (19.97,-0.5) coordinate (p1) {};
    %\path (13.56,-0.5) coordinate (p2) {};
    %\path (19.97,0.5) coordinate (p3) {};
    %\path (13.56,0.5) coordinate (p4) {};
    \fill[shade,bottom color=Cerulean,top color=Cerulean] (p1) -- (p2) -- (p4) -- (p3);
\end{tikzpicture}
\makeheading{Matthew Aaron Miller}
\begin{minipage}[b][25cm][t]{\dimexpr0.65\textwidth}
    \bigbreak
    \section*{Experience}
   \hrefgreen{http://www.teamsparq.com/}{\textbf{Sparq}} - Atlanta, Georgia (Remote)
\begin{outerlist}
    \item[] \textbf{Senior Consultant} \hfill  March 2022 - Present
     \begin{innerlist}
      \item Contributed to an API for a health coaching company in Java on AWS.
      \item Team Lead for a small group working on Java microservices for a client in call center management.
     \end{innerlist}
    \end{outerlist}
    \blankline

    \hrefgreen{http://www.gotsoccer.com/}{\textbf{GotSoccer LLC}} - Neptune Beach, Florida (Remote)
    \begin{outerlist}
    \item[] \textbf{Optimization Expert} \hfill  February 2019 - February 2022
     \begin{innerlist}
      \item Solved professional sports scheduling problems modeled as MILPs in Gurobi and CPLEX.
      \item Developed constraints and algorithms for a Python library used to solve scheduling problems.
      \item Built a custom simulated annealing solver in Java for the NBA scheduling problem.  
      \item Learned Ruby on Rails in order to contribute to web platform integration of pro scheduling system.
      \item Created a hybrid ticket scanning app for Android and IOS using Ionic/Capacitor and Typescript.     
     \end{innerlist}
    \end{outerlist}
    \blankline

    \hrefgreen{http://www.sagekey.com/}{\textbf{SageKey Software}} - Penticton, British Columbia (Remote)
    \begin{outerlist}
    \item[] \textbf{Software Engineer} \hfill  August 2018 - December 2018
     \begin{innerlist}
      \item Built an auto part selection system for transmission schematics in .NET, Elastic, and JS; then integrated it into a Magento store.
     \end{innerlist}
    \end{outerlist}
    \blankline

    \hrefgreen{http://www.xeratec.com/}{\textbf{Xeratec Corporation}} - Hancock, Michigan
    \begin{outerlist}
    \item[] \textbf{Software Engineer} \hfill  November 2013 - August 2018
     \begin{innerlist}
      \item Maintained and extended a Java EE application for a client in the insurance industry.
      \item Lead programmer on a Java based project using Spring, MS SQL, and Angular for a client in pharmaceutical warehousing.
      \item Technical lead on a Windows based civil engineering application in Visual C++.  
      \item Worked on several .NET web applications using MS web frameworks and SQL Server.
     \end{innerlist}
    \end{outerlist}
    \blankline

    \hrefgreen{http://www.signatureresearchinc.com/}{\textbf{Signature Research}} - Calumet, Michigan
    \begin{outerlist}
    \item[] \textbf{Software Engineer I} \hfill  January 2011 - March 2013
     \begin{innerlist}
      \item Contributed extensively to a physics based temperature prediction and hyperspectral raytracing project capable of generating imagery for any band from thermal to visible.
      \item Worked with a highly object oriented code base equipped with both multiprocessing and threading capabilities.
      \item Became familiar with meteorological data and simulations including atmospheric radiation and transmission modeling with \hrefgreen{http://www.modtran5.com/}{MODTRAN}.
      \item Implemented several mathematical models for phenomena including ocean waves, cumulus clouds, material based surface reflections, and polarized light. 
     \end{innerlist}
    \end{outerlist}
    \blankline

    \hrefgreen{http://www.imtek.de/}{\textbf{IMTEK, Albert-Ludwigs-Universit\"{a}t}} - Freiburg, Germany
    \begin{outerlist}
     \item[] \noindent {\bf Research Assistant} \hfill January 2009 - July 2009
     \begin{innerlist}
      \item Attempted to add MPI parallelization to a general purpose particle dynamics code written in C++ with OpenMP. 
     \end{innerlist}
    \end{outerlist}
    \blankline
        
    \hrefgreen{http://www.signatureresearchinc.com/}{\textbf{Signature Research}} - Calumet, Michigan
    \begin{outerlist}
    \item[] \textbf{Software Developer} \hfill  April 2008 - September 2008
     \begin{innerlist}
      \item Worked with a senior researcher to design an image reconstruction algorithm.
      \item Created an application for resizing DEM raster data using different interpolation and smoothing algorithms.
     \end{innerlist}
    \end{outerlist}
    \blankline

    \textbf{Army High Performance Computing Research Center} - Minneapolis, Minnesota
    \begin{outerlist}
    \item[] \textbf{Student Intern} \hfill June 2005 - August 2005
    \begin{innerlist}
     \item Completed a short research project in computational fluid dynamics. 
     \item Aided other interns to learn about computing on a Cray X1. 
    \end{innerlist}
    \end{outerlist}
\end{minipage}
\hfill
\fcolorbox{Cerulean}{Cerulean}{%
\begin{minipage}[b][25cm][t]{0.3\textwidth}
  \bigbreak
  \section*{Contact}
    \begin{outerlist2}
    \item[] (906) 281-4210
    \item[] \hrefblack{mailto:mtthwamllr@gmail.com}{mtthwamllr@gmail.com} 
    \item[] \hrefblack{https://github.com/up-busab}{https://github.com/up-busab}
    %\item[] 1001 Tenth Avenue, Houghton MI, 49931 
    \end{outerlist2}
  \bigbreak
  \section*{Skills}
    \begin{outerlist}
    \item[] \textbf{Code Polyglot}
      \begin{innerlist}
        \item[] \raggedright C \tpc C++ \tpc Python \tpc Java \tpc C\# \tpc Fortran \tpc 
          TypeScript \tpc JavaScript \tpc Ruby \tpc Visual Basic \tpc PHP 
      \end{innerlist}    
  \item[] \textbf{Mathematical Programming}
      \begin{innerlist}
        \item[] \raggedright Gurobi \tpc CPLEX \tpc Mathematica \tpc Matlab \tpc FFTW 
      \end{innerlist}
     \item[] \textbf{Databases}
      \begin{innerlist}
        \item[] \raggedright Postgres \tpc MariaDB \tpc MS SQL \tpc MongoDB \tpc Elasticsearch 
      \end{innerlist}
    \item[] \textbf{Devops \& Build Systems}
      \begin{innerlist}
        \item[] \raggedright Docker \tpc Kubernetes \tpc Maven \tpc make \tpc Travis \tpc CircleCI \tpc Github Actions 
      \end{innerlist}
  \item[] \textbf{Graphics \& GUI}
      \begin{innerlist}
        \item[] \raggedright OpenGL \tpc SDL \tpc QT \tpc Mitsuba \tpc POVRay \tpc Visual C++ 
      \end{innerlist}
    \item[] \textbf{Parallel Programming}
      \begin{innerlist}
        \item[] \raggedright MPI \tpc OpenMP \tpc PThreads \tpc NVIDIA CUDA \tpc UPC 
      \end{innerlist}   
    \item[] \textbf{Web Frameworks}
      \begin{innerlist}
        \item[] \raggedright Spring/Spring Boot \tpc .NET \tpc Rails \tpc Magento
      \end{innerlist}       
    \item[] \textbf{Frontend \& Mobile Technologies}
      \begin{innerlist}
        \item[] \raggedright Angular \tpc HTML 5 \tpc CSS \tpc Bootstrap \tpc Ionic/Capacitor \tpc JQuery
      \end{innerlist}
    \end{outerlist}
  \bigbreak
  \section*{Education}
    \begin{outerlist}
    \item[] \raggedright \textbf{M.S. - Mathematics}
        \linebreak
        \hrefblack{http://www.mtu.edu/}{Michigan Tech}, 2008
        \begin{innerlist}
         \item Combinatorics \& Algebra  
         \item Algorithms \& High Performance Computing
        \end{innerlist}
    \item[] \raggedright \textbf{B.S. - Mathematics}
        \linebreak
        \hrefblack{http://www.mtu.edu/}{Michigan Tech}, 2006
        \begin{innerlist}
            \item Minor in Computer Science
        \end{innerlist}
    \end{outerlist}
\end{minipage}}

\end{document}

