\newcommand{\mycontact}
{
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{2.5in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
1001 Tenth Avenue & (906) 281-7277  \\
Houghton, MI, 49931 & \href{mailto:mtthwamllr@gmail.com}{mtthwamllr@gmail.com} \\
                   & \href{https://github.com/up-busab}{https://github.com/up-busab} \\
\end{tabular}
}

\newcommand{\myobjective}{ To obtain a position in software or simulation. I enjoy working on teams, software quality, learning new technologies, and solving problems from many different domains.}

\newcommand{\myeducation}{
\href{http://www.mtu.edu/}{\textbf{Michigan Technological University}} - Houghton, Michigan 
\begin{outerlist}
\item[] M.S.,
        \href{http://www.math.mtu.edu/}{Mathematics}, December 2008        
        \begin{innerlist}
         \item Report: \textit{Implementing and Understanding Algorithms in Unified Parallel C}
%         \item Adviser: \href{http://www.math.mtu.edu/~merk/}{Dr. Philip R. Merkey}
        \end{innerlist}

\item[] B.S.,
        \href{http://www.math.mtu.edu/}{Mathematics}, August 2006        
        \begin{innerlist}
         \item Minor in \href{http://www.cs.mtu.edu/}{Computer Science}
        \end{innerlist}

\end{outerlist}
}

\newcommand{\myawards}{need to get me some o deez}

\newcommand{\myinterests}{ thinking }

\newcommand{\myteaching}
{
\href{http://www.finlandia.edu/}{\textbf{Finlandia University}} - Hancock, Michigan
\begin{outerlist}
\item[] \textbf{Adjunct Instructor} \hfill August 2010 - December 2010 
    \begin{innerlist}
        \item Delivered weekly lectures in addition to developing and grading exams and homework sets.      
        \item Taught two sections of elementary algebra and worked in the tutoring center.
    \end{innerlist}
\end{outerlist}
\blankline

\href{http://www.mtu.edu}{\textbf{Michigan Technological University}} - Houghton, Michigan
\begin{outerlist}
\item[] \textbf{Graduate Student/Adjunct Instructor} \hfill Autumn 2006 - Spring 2010 
    \begin{innerlist}
        \item Delivered weekly lectures in addition to developing and grading exams and homework sets. 
        \item Taught several different courses ranging from elementary algebra to second semester calculus.
%        \begin{innerlist}
%	 \item MA2160:  Calculus II with Technology (Spring 2009)
%	 \item MA1161:  Calculus I with Technology (Spring/Autumn 2007, Spring 2010)
%	 \item MA1032:  Data, Functions, and Graphs (Autumn 2008, Spring 2009)
%        \end{innerlist}
%	\item Hired as adjunct instructor for MA1032 and MA2160 during the Spring of 2009.
    \end{innerlist}

\item[] \textbf{Math Lab Course Coordinator} \hfill Spring/Summer 2008, Autumn 2009
    \begin{innerlist}
     %   \item Collaborated with faculty in the design and implementation of \href{http://www.wolfram.com/}{Mathematica} Labs and Blackboard online quizzes for Calculus I,II, and III.
	    \item Managed and instructed undergraduate lab TA's.
        \item Oversaw automated assignment and grading procedures for over 1200 students. 
    \end{innerlist}

\item[] \textbf{Grader} \hfill Summer 2007
    \begin{innerlist}
        \item Graded programs written by students for a graduate level course in scientific programming.
    \end{innerlist}
\end{outerlist}
\blankline
}

\newcommand{\myrecentprojobs}
{
\href{http://www.ruralsourcing.com/}{\textbf{Rural Sourcing}} - Atlanta, Georgia (Remote)
\begin{outerlist}
\item[] \textbf{Senior Consultant} \hfill  March 2022 - Present
 \begin{innerlist}
  \item Team Lead for a small group working on Java microservices for a client in call center management.
 \end{innerlist}
\end{outerlist}
\blankline

\href{http://www.gotsoccer.com/}{\textbf{GotSoccer LLC}} - Neptune Beach, Florida (Remote)
\begin{outerlist}
\item[] \textbf{Optimization Expert} \hfill  February 2019 - February 2022
 \begin{innerlist}
  \item Solved professional sports scheduling problems modeled as MILPs in Gurobi and CPLEX.
  \item Devloped constraints and algorithms for a Python library used to solve scheduling problems.
  \item Built a custom simulated annealing solver in Java for the NBA scheduling problem.  
  \item Learned Ruby on Rails in order to contribute to web platform integration of pro scheduling system.
  \item Created a hybrid ticket scanning app for Android and IOS using Ionic/Capacitor and Typescript.     
 \end{innerlist}
\end{outerlist}
\blankline

\href{http://www.sagekey.com/}{\textbf{SageKey Software}} - Penticton, British Columbia (Remote)
\begin{outerlist}
\item[] \textbf{Software Engineer} \hfill  August 2018 - December 2018
 \begin{innerlist}
  \item Built an auto part selection system for transmission schematics in .NET, Elastic, and JS; then integrated it into a Magento store.
 \end{innerlist}
\end{outerlist}
\blankline

\href{http://www.xeratec.com/}{\textbf{Xeratec Corporation}} - Hancock, Michigan
\begin{outerlist}
\item[] \textbf{Software Engineer} \hfill  November 2013 - August 2018
 \begin{innerlist}
  \item Maintained and extended a Java EE application for a client in the insurance industry.
  \item Lead programmer on a Java based project using Spring, MS SQL, and Angular for a client in pharmaceutical warehousing.
  \item Technical lead on a Windows based civil engineering application in Visual C++.  
  \item Worked on several .NET web applications using MS web frameworks and SQL Server.
 \end{innerlist}
\end{outerlist}
\blankline
}

\newcommand{\mypastprojobs}
{
\href{http://www.signatureresearchinc.com/}{\textbf{Signature Research}} - Calumet, Michigan
\begin{outerlist}
\item[] \textbf{Software Engineer I} \hfill  January 2011 - March 2013
 \begin{innerlist}
  \item Contributed extensively to a physics based temperature prediction and hyperspectral raytracing project capable of generating imagery for any band from thermal to visible.
  \item Worked with a highly object oriented code base equipped with both multiprocessing and threading capabilities.
  \item Became familiar with meteorological data and simulations including atmospheric radiation and transmission modeling with \href{http://www.modtran5.com/}{MODTRAN}.
  \item Implemented several mathematical models for phenomena including ocean waves, cumulus clouds, material based surface reflections, and polarized light. 
 \end{innerlist}
\end{outerlist}
\blankline

\href{http://www.imtek.de/}{\textbf{IMTEK, Albert-Ludwigs-Universit\"{a}t}} - Freiburg, Germany
\begin{outerlist}
 \item[] \noindent {\bf Research Assistant} \hfill January 2009 - July 2009
 \begin{innerlist}
  \item Attempted to add MPI parallelization to a general purpose particle dynamics code written in C++ with OpenMP. 
 \end{innerlist}
\end{outerlist}
\blankline
	
\href{http://www.signatureresearchinc.com/}{\textbf{Signature Research}} - Calumet, Michigan
\begin{outerlist}
\item[] \textbf{Software Developer} \hfill  April 2008 - September 2008
 \begin{innerlist}
  \item Worked with a senior researcher to design an image reconstruction algorithm.
  %\item Implemented and tested the above algorithm on a Beowulf cluster. 
  \item Created an application for resizing DEM raster data using different interpolation and smoothing algorithms.
 \end{innerlist}
\end{outerlist}
\blankline

\textbf{Army High Performance Computing Research Center} - Minneapolis, Minnesota
\begin{outerlist}
\item[] \textbf{Student Intern} \hfill June 2005 - August 2005
\begin{innerlist}
 \item Completed a short research project in computational fluid dynamics. 
 \item Aided other interns to learn about computing on a Cray X1. 
% \item Obtained DOD clearance for the summer.
\end{innerlist}
\end{outerlist}
}

\newcommand{\myretailjobs}
{
\href{http://www.bookstore.mtu.edu/michtech2}{\textbf{University Images}} - Houghton, Michigan
\begin{outerlist}
\item[] \textbf{Sales Clerk} \hfill  November 2002 - January 2003
 \begin{innerlist}
  \item Operated a cash register, assisted with inventory, and closed the store.
 \end{innerlist}
\end{outerlist}
}

\newcommand{\mypublications}{\begin{bibsection} \end{bibsection} }

\newcommand{\mypresentations}
{
\begin{outerlist}
\item[] \textit{The FFTW and NVIDIA CUDA CUFFT Libraries}
\begin{innerlist}
\item[] Lecture in CS5331: Parallel Algorithms, Michigan Technological University (2009)
\end{innerlist}
\item[] \textit{Effect of Fractal Dimension in a Nanoparticle Growth Simulation}
\begin{innerlist}
\item[] Final Presentation, Summer Institute 2005, AHPCRC (2005)
\end{innerlist}
\end{outerlist}
}

\newcommand{\mytechs}
{
\begin{outerlist}
\item[] Modeling optimization problems as MILPs using Gurobi or Cplex in Python.
\item[] Scientific programming in C, C++, Modern C++, Fortran, Matlab, and Mathematica.
\item[] Java web application programming using Spring, Maven, MyBatis, Hibernate; deployment on Tomcat servers.
\item[] Fullstack web development on other platforms such as Ruby on Rails and PHP.
\item[] Database work in SQL on MS SQL Server, MySQL, and SQLite; including TSQL stored procedures.
\item[] Obsession with using Docker to package runtime environments and complicated build systems.
\item[] Experience using continuous integration platforms such as CircleCI and Travis.    
\item[] Frontend web development for in HTML5, CSS, JS, JQuery, Angular, and Bootstrap. 
\item[] Mobile app development for Android and IOS using Ionic/Capacitor and Typescript
\item[] Rules engine development in JBoss Enterprise BRMS (Drools).
\item[] Experience with .NET web frameworks such as ASP.NET and MS MVC; deployment on IIS
\item[] .NET programming in C\#, VB, and VC++; including work with Entity Framework.  
\item[] Integration work in MS SSIS and SSAS; reporting in SSRS and Telerik Reports.
\item[] Parallel programming on clusters and shared memory architectures in Unified Parallel C, MPI, OpenMP, and NVIDIA CUDA.
\item[] A broad range of mathematical subjects including advanced calculus, theoretical and numerical linear algebra, and PDEs.
\item[] Discrete mathematics, including combinatorics, abstract algebra, and algorithms.
\item[] 3D computer graphics and GUI creation using OpenGL, SDL, and QT.
\item[] Familiarity with Linux and use of scientific libraries such as FFTW and GSL. 
\item[] Fluent in \LaTeX{} and noweb systems for documents and presentations.
\end{outerlist}
}

\newcommand{\mypeds}
{
\begin{outerlist}
\item[] Document preparation for worksheets, quizzes, and exams using \LaTeX{}.
\item[] Graphics creation in \href{http://www.wolfram.com/}{Mathematica} and \href{http://www.povray.org/}{POV-ray}.
\item[] Dynamic animations for classroom use in \href{http://www.wolfram.com/}{Mathematica}.
\item[] Website creation and management in HTML.
\end{outerlist}
}

\newcommand{\myproref}{

Walter Sebastian Gisler
Head of GotPro/Optimization
GotSoccer LLC
walter@gotsport.com
\\
Aaron Wilmoth
Chief Technical Officer
GotSoccer LLC
aaron@gotsport.com
\\
%James Mertens\\
%Senior Software Engineer/Architect\\
%Xeratec Corporation (Formerly)\\
%401 Hancock St\\
%Hancock, MI 49930\\
%906.482.6765\\
%james.mertens@xeratec.com\\
%\\
%Ken Byers\\
%Senior Software Engineer/Chapter Lead\\
%Xeratec Corporation\\
%401 Hancock St\\
%Hancock, MI 49930\\
%906.482.6765\\
%ken.byers@xeratec.com\\
%\\
%Denise Talcott\\
%Manager of Scientific Computing\\
%Signature Research, Inc.\\ 
%P.O. Box 346\\
%56905 Calumet Avenue\\
%Calumet, MI 49913\\
%906.337.3360\\
%talcott@signatureresearchinc.com\\
%\\
%Larry Coke\\
%Head Scientist\\
%Signature Research, Inc.\\ 
%P.O. Box 346\\
%56905 Calumet Avenue\\
%Calumet, MI 49913\\
%906.337.3360\\
%coke@signatureresearchinc.com\\
%\\
%Philip R. Merkey, Ph.D.\\
%Parallel Computing Researcher\\
%merk@mtu.edu\\
%\\
%John Hilgers, Ph.D.\\
%Researcher\\
%Signature Research, Inc.\\ 
%P.O. Box 346\\
%56905 Calumet Avenue\\
%Calumet, MI 49913\\
%906.337.3360\\
%hilgers@signatureresearchinc.com\\
%\\
%Barbara Bertram, Ph.D.\\
%Professor of Mathematics, retired\\
%1201 7th Avenue\\
%Houghton, MI 49931\\
%906.482.6416\\
}


